Four reasons your build is slow

### 2019-01-16 paper.tex
adding figures and working on zstd section

@@

An example of a project with such a build is Facebook's zstd project \cite{}.  If we use our tool
to analyse the span of zstd's build, we see that the original span is dominated by a single call
to cc.
\begin{verbatim}
  cc -I../lib -I../lib/common -I../lib/compress -I../lib/dictBuilder -DXXH_NAMESPACE=ZSTD_ -I../lib/legacy -DZSTD_LEGACY_SUPPORT=5 -O3 -DBACKTRACE_ENABLE=0 ../lib/common/debug.c ../lib/common/entropy_common.c ../lib/common/error_private.c ../lib/common/fse_decompress.c ../lib/common/pool.c ../lib/common/threading.c ../lib/common/xxhash.c ../lib/common/zstd_common.c ../lib/compress/fse_compress.c ../lib/compress/hist.c ../lib/compress/huf_compress.c ../lib/compress/zstd_compress.c ../lib/compress/zstd_double_fast.c ../lib/compress/zstd_fast.c ../lib/compress/zstd_lazy.c ../lib/compress/zstd_ldm.c ../lib/compress/zstd_opt.c ../lib/compress/zstdmt_compress.c ../lib/decompress/huf_decompress.c ../lib/decompress/zstd_decompress.c ../lib/dictBuilder/cover.c ../lib/dictBuilder/divsufsort.c ../lib/dictBuilder/fastcover.c ../lib/dictBuilder/zdict.c ../lib/legacy/zstd_v05.c ../lib/legacy/zstd_v06.c ../lib/legacy/zstd_v07.c zstdcli.o fileio.o bench.o datagen.o dibio.o -o zstd
\end{verbatim}

@@

\begin{verbatim}
cc -I. -I./common -DXXH_NAMESPACE=ZSTD_ -I./legacy -DZSTD_LEGACY_SUPPORT=5 -O3 common/debug.c common/entropy_common.c common/error_private.c common/fse_decompress.c common/pool.c common/threading.c common/xxhash.c common/zstd_common.c compress/fse_compress.c compress/hist.c compress/huf_compress.c compress/zstd_compress.c compress/zstd_double_fast.c compress/zstd_fast.c compress/zstd_lazy.c compress/zstd_ldm.c compress/zstd_opt.c compress/zstdmt_compress.c decompress/huf_decompress.c decompress/zstd_decompress.c deprecated/zbuff_common.c deprecated/zbuff_compress.c deprecated/zbuff_decompress.c dictBuilder/cover.c dictBuilder/divsufsort.c dictBuilder/fastcover.c dictBuilder/zdict.c legacy/zstd_v05.c legacy/zstd_v06.c legacy/zstd_v07.c -shared -fPIC -fvisibility=hidden -Wl,-soname=libzstd.so.1 -o libzstd.so.1.3.7
\end{verbatim}

If their of these calls were members of the build's span, than our tool predicts the span would be
7.2 seconds rather than 39 seconds or 37 seconds (todo check that time).  To test this we manually
replaced the original calls with many calls that first compiled each file individually then later
linked them.  % todo fill in results.

@@

>>>>

\begin{figure}[t]
  \includegraphics[width=0.5\textwidth]{zstd-speedup}
  \caption{todo}
  \label{fig:zstd}
\end{figure}

@@

An example of a project with such a build is Facebook's zstd project \cite{}.  If we use our tool
to analyse the span of zstd's build, we see that the original span is dominated by a single call
to cc.

\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
  cc -I../lib -I../lib/common -I../lib/compress -I../lib/dictBuilder 
     -DXXH\_NAMESPACE=ZSTD\_ -I../lib/legacy -DZSTD\_LEGACY\_SUPPORT=5 -O3 
     -DBACKTRACE\_ENABLE=0 
     ../lib/common/debug.c ../lib/common/entropy\_common.c ../lib/common/error\_private.c 
     ../lib/common/fse\_decompress.c ../lib/common/pool.c ../lib/common/threading.c 
     ../lib/common/xxhash.c ../lib/common/zstd\_common.c ../lib/compress/fse\_compress.c 
     ../lib/compress/hist.c ../lib/compress/huf\_compress.c 
     ../lib/compress/zstd\_compress.c ../lib/compress/zstd\_double\_fast.c 
     ../lib/compress/zstd\_fast.c ../lib/compress/zstd\_lazy.c 
     ../lib/compress/zstd\_ldm.c ../lib/compress/zstd\_opt.c 
     ../lib/compress/zstdmt\_compress.c ../lib/decompress/huf\_decompress.c 
     ../lib/decompress/zstd\_decompress.c ../lib/dictBuilder/cover.c 
     ../lib/dictBuilder/divsufsort.c ../lib/dictBuilder/fastcover.c 
     ../lib/dictBuilder/zdict.c ../lib/legacy/zstd\_v05.c ../lib/legacy/zstd\_v06.c 
     ../lib/legacy/zstd\_v07.c zstdcli.o fileio.o bench.o datagen.o dibio.o -o zstd
\end{Verbatim}

@@

\begin{verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
cc -I. -I./common -DXXH_NAMESPACE=ZSTD_ -I./legacy -DZSTD_LEGACY_SUPPORT=5 -O3 common/debug.c common/entropy_common.c common/error_private.c common/fse_decompress.c common/pool.c common/threading.c common/xxhash.c common/zstd_common.c compress/fse_compress.c compress/hist.c compress/huf_compress.c compress/zstd_compress.c compress/zstd_double_fast.c compress/zstd_fast.c compress/zstd_lazy.c compress/zstd_ldm.c compress/zstd_opt.c compress/zstdmt_compress.c decompress/huf_decompress.c decompress/zstd_decompress.c deprecated/zbuff_common.c deprecated/zbuff_compress.c deprecated/zbuff_decompress.c dictBuilder/cover.c dictBuilder/divsufsort.c dictBuilder/fastcover.c dictBuilder/zdict.c legacy/zstd_v05.c legacy/zstd_v06.c legacy/zstd_v07.c -shared -fPIC -fvisibility=hidden -Wl,-soname=libzstd.so.1 -o libzstd.so.1.3.7
\end{verbatim}

If neither of these calls were members of the build's span, then our tool predicts the span would be
7.2 seconds rather than 39 seconds or 37 seconds.  To test this we manually replaced the first of
these two cc calls with 28 new calls to cc; 27 of those are spent compiling each .c file individually
and the last is to link them all together.  Due to this new organization the 27 .c files can be
compiled in parallel.  Similarly, the second cc call is replace with 28 new calls to cc; 27 of which
compile each .c file individually and the last of which links the object files together.

You can see in figure \ref{fig:zstd} that when we ran the modified build with 1 to 32 jobs we
observed the predicted speedup.  An additional performance improvement that we did not predict was
that the work of the new build would decrease from approximately 120 seconds to approximately 80 seconds.

Each of the generated object files is declared as its own target; so when make considers building
each object file it can check if the file already exists and whether it must be rebuilt.  It turns
out that the object files being built as part of the first long cc command, had already been
previously built by make.  By declaring each object file as its own target and building each one
individually then linking them, make was able to determine it wasn't necessary to build them the
2nd time; so the effect time of the first cc command when from 40 seconds to 2 seconds; only the
time necessary for linking the object files together.

@@

\begin{figure}[]
  \includegraphics[width=0.5\textwidth]{llvm-speedup}
  \caption{todo}
  \label{fig:llvm}
\end{figure}
